### 2018-12-13 supplements/KineticsTable/kinetics_table.tex
updated simulations for competitions
Discussion under  revision, preparing models for submission. Both tasks not yet finished

\subsection*{Amount of enzymes and import rates}
The total enzyme concentration was set to 10 times the scaling factor, for all enzymes except NamPT and NMNAT, for which the concentration was set to 100 times the scaling factor. As enzyme concentrations here have an arbitrary unit a scaling factor of 0.1$\mu$M  was applied to all enzymatic reactions to achieve consumption rates that are in the range of reported values  \cite{Liu2018}. Concentration of potential co-substrates were assumed to be constant and not-limiting for the reaction. Thus being implicitly represented by maximal velocities consiting of total enzyme concentration times tunrover rates. Nam import rates for import into the system was set to 0.1 $\mu$M/s for all simulations, being in the range meassured for Nam uptake in mammalian cells \cite{Namuptake}. For the two compartment simulation compartmentsize was equal to ... for both compartments. The Nam import rates were set to 100/s for both compartments. The amount of NADA present was set to 100. Thus equal to the amount of NamPT used.

>>>>

\subsection*{Amount of enzymes and import rates}
The total enzyme concentration was set to 10 times the scaling factor, for all enzymes except NamPT and NMNAT, for which the concentration was set to 100 times the scaling factor. As enzyme concentrations here have an arbitrary unit a scaling factor of 0.1$\mu$M  was applied to all enzymatic reactions to achieve consumption rates that are in the range of reported values  \cite{Liu2018}. Concentration of potential co-substrates were assumed to be constant and not-limiting for the reaction. Thus being implicitly represented by maximal velocities consisting of total enzyme concentration times tunrover rates. Nam import rates for import into the system was set to 0.1 $\mu$M/s for all simulations, being in the range meassured for Nam uptake in mammalian cells \cite{Namuptake}. In addition to the reactions listed above an additional NAD consumption was simulated using HMM-kinetics with a susbtrate affinity of 0.3 mM and a turnover rate of 1. Furthermore, reversible NAD binding to proteins was simulated using reversible mass actions kinetics with an equilibrium constant of 0.1, which is in a range of values reported in the literature, dissociation and association constants where set to 10 and 100$s^{-1}$ respectively.
s
For the two compartment simulation, compartmentsize was equal for both compartments and set to 1$\mu$l. The actual compartmentsize does not change the outcome of the simulations as long as both compartments have equal volumes. The Nam import rates were set to 100$s^{-1}$ for both compartments. The amount of NADA present was set to 100. Thus equal to the amount of NamPT used.
